### 2021-03-27 papers.tex
listed all on-time papers w/ correct author names

\addtrack
	{}{Big Dummy Track}
\addpaper
	{Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
	{Nicolas Hurtubise}
	{Keywords: component, formatting, style, styling, insert}
	{SIGBOVIK_2021_paper_1}
	{0cm}
	{}
\addpaper
	{Stop Doing Type Theory}
	{Jason Reed}
	{Keywords: Ranting, Raving, Muttering, Grumbling}
	{SIGBOVIK_2021_paper_2}
	{0cm}
	{}

@@

	{Dylan Ashley, Anssi Kanervisto and Brendan Bennett}

@@

	{Shane Guan, Skanda Kaashyap and Blair Chen}

@@

	{Fred Buchanan, Sam Cohen and James Flamino}

@@

	{Bernhard Egger, Kevin Smith and Max Siegel}

@@

	{Vinay Prabhu}

@@

	{Efrati Benjamin}

@@

	{Mary Shaw}

@@

>>>>

\addtrack
	{}{Big Dummy Track}
\addpaper
	{Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
	{Nicolas Hurtubise} %TODO: those other authors???
	{Keywords: component, formatting, style, styling, insert}
	{SIGBOVIK_2021_paper_1}
	{0cm}
	{}
\addpaper
	{Stop Doing Type Theory}
	{}
	{Keywords: Ranting, Raving, Muttering, Grumbling}
	{SIGBOVIK_2021_paper_2}
	{0cm}
	{}

@@

	{Dylan R. Ashley, Anssi Kanervisto and Brendan Bennett}

@@

	{Shane Guan, Blair Chen, Skanda Kaashyap}

@@

	{Prophet \#1, Prophet \#2 and Prophet \#3}

@@

	{Bernhard Egger, Kevin Smith and Max Siegel} %TODO: put in crossed out David Cox?

@@

	{Vinay Uday Prabhu}

@@

@@

	{Diogenes}

@@

	{A Note on ``The Consent Hierarchy''}
	{Anonymous Nobody}
	{Keywords: freely given, reversible, informed, enthusiastic, specific}
	{SIGBOVIK_2021_paper_25}
	{Lowestcase and uppestcase letters: Advances in derp learning}
	{Tom Murphy VII}
	{case analysis, derp learning, 3d manifold, chess, exponentiation, fonts}
	{SIGBOVIK_2021_paper_26}

\addpaper
	{Soliterrible}
	{Sam Stern}
	{Keywords: solitaire, klondike, cards}
	{SIGBOVIK_2021_paper_27}
	{0cm}
	{}
	{Another Thorough Investigation of the Degree to which the COVID-19 Pandemic has Enabled Subpar-Quality Papers to Make it into SIGBOVIK, by Reducing the Supply of Authors Willing to Invest the Necessary Effort to Produce High-Quality Papers}
	{Shalin Shah}
	{Keywords: SIGBOVIK, COVID-19, Lazy, Low-Effort, Subpar-Quality}
	{SIGBOVIK_2021_paper_28}
	{Spacecraft Attitude Determination and Control}
	{Freddie Rawlins}
	{Keywords: attitude, determination, happy satellites}
	{SIGBOVIK_2021_paper_29}
	{A Complete Survey of 0-Dimensional Computer Graphics}
	{Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Ryan Po}
	{Keywords: Computer Graphics, Geometry, Rendering, Animation}
	{SIGBOVIK_2021_paper_30}
	{Macro-driven metalanguage for writing Pyramid Scheme programs}
	{Marcin Konowalczyk}
	{Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
	{SIGBOVIK_2021_paper_31}
	{On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
	{Zikuan Wang}
	{Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
	{SIGBOVIK_2021_paper_32}
	{On the dire importance of MRU caches for human survival (against Skynet)}
	{Darío de la Fuente García, Félix Áxel Gimeno Gil, Juan Carlos Morales Vega and Borja Rodríguez Gálvez}
	{Keywords: Skynet, MS paint, cache, MRU, dMRU, sMRU, NEP}
	{SIGBOVIK_2021_paper_33}
	{Dependent Stringly-Typed Programming}
	{G. Allais}
	{Keywords: dependent stringly typed programming, best practices, agda}
	{SIGBOVIK_2021_paper_34}
	{Tensorflow for Abacus Processing Units}
	{Robert McCraith}
	{Keywords: machine learning, tensor flow, abacus, mathematics, calculus, differentiation, computation}
	{SIGBOVIK_2021_paper_35}
	{Critical Investigations on Avians: Surveillance, Computational Amorosities, and Machines}
	{Brandon Bohrer and Connie Chau}
	{Keywords: Birds, Not, Real}
	{SIGBOVIK_2021_paper_36}
	{NetPlop: A moderately-featured presentation editor built in NetLogo}
	{Patrick Steinmann}
	{Keywords: agent-based slideshows, slide-based models, singularity}
	{SIGBOVIK_2021_paper_37}
	{RadicAI: A Radical, Though Not Entirely New, Approach to AI Paper Naming}
	{James McCann and Mike McCann}
	{SIGBOVIK_2021_paper_38}
	{Story Time}
	{James McCann and Mike McCann}
	{Keywords: story time, time for stories, the time of stories, stories? it's time, our time is now our time is stories, big data? I get it.}
	{SIGBOVIK_2021_paper_39}
	{If It Type-checks, It Works: FoolProof Types As Specifications}
	{Brandon Wu}
	{Keywords: PL, languages, types, specifications, correctness, type-checking, functional programming}
	{SIGBOVIK_2021_paper_40}
	{The Newcomb-Benford Law, Applied to Binary Data: An Empirical and Theoretic Analysis}
	{Gabriel Chuang and Brandon Wu}
	{Keywords: Numerical Methods, Verification, Poor Proof Style, Statistics}
	{SIGBOVIK_2021_paper_41}
	{What Lothar Collatz Thinks of the CMU Computer Science Curriculum}
	{Gabriel Chuang and Brandon Wu}
	{Pedagogy, Precognition, Theoretical Computer Science, Coincidences, Sequences, Category Theory, Computability}
	{SIGBOVIK_2021_paper_42}
	{On the Origin of Species of Self-Supervised Learning}
	{Samuel Albanie, Erika Lu and Joao Henriques}
	{Keywords: self-supervised learning, origin of species, artificial naturalism}
	{SIGBOVIK_2021_paper_43}
	{Opening Moves in 1830: Strategy in Resolving the N-way Prisoner’s Dilemma}
	{Philihp Busby and Daniel Ribeiro E Sousa}
	{Keywords: boardgame, opening, strategy, deterministic, auction}
	{SIGBOVIK_2021_paper_44}

\addreview
	{SIGBOVIK_2021_review_1}
	{0cm}
